% = Commands for suppressing page numbers for unused glossary entries

\newcommand*{\glsgobblenumber}[1]{}

\makeatletter
%% lockstep's code
\newcommand*{\glsaddnp}[2][]{%
  \glsdoifexists{#2}%
  {%
%     \def\@glsnumberformat{glsnumberformat}% DELETED
    \def\@glsnumberformat{glsgobblenumber}% NEW
    \edef\@gls@counter{\csname glo@#2@counter\endcsname}%
    \setkeys{glossadd}{#1}%
    \@gls@saveentrycounter
    \@do@wrglossary{#2}%
  }%
}

\@ifundefined{glsaddallunused}{
  %% new code; modified \glsaddall
  \newcommand{\glsaddallunused}[1][]{%
    \edef\@glo@type{\@glo@types}%
    \setkeys{glossadd}{#1}%
    \forallglsentries[\@glo@type]{\@glo@entry}{%
      \ifglsused{\@glo@entry}{}{%
       \glsaddnp[#1]{\@glo@entry}}}%
  }
}{}
\makeatother


% = Acronym Definition
\newcommand{\lsad}[3]{ % Label, Acronym, Definition
  \newacronym{#1}{\texttt{#2}}{#3}
}

% = Glossary Entry
\newcommand{\lsge}[3]{ % Label, Acronym, Definition
  \newglossaryentry{#1}{
    name=#2,
    description={#3}
  }
}

% Glossary Entries

\lsge{deployment}{Deployment}{The process of moving software that is developed on a local machine to a remote server.}
\lsge{django}{Django}{A popular Python web application framework.}
\lsge{bundler}{Bundler}{A Ruby dependency manager whose packages are called ``gems''.}
\lsge{gem}{Gem}{A \gls{bundler} Package.}
\lsge{javascript}{JavaScript}{The standard client-side script programming language used in web development.}
\lsge{coffeescript}{CoffeeScript}{A programming language that transcompiles to JavaScript. Uses a modern syntax similar to Ruby or Python.}
\lsge{sproutcore}{SproutCore}{A popular JavaScript web application framework, a precursor to Ember.js.}
\lsge{emberjs}{Ember.js}{A modern client-side JavaScript web application framework.}
\lsge{apache}{Apache HTTP Server}{The classic de-facto standard HTTP server.}
\lsge{nginx}{NginX}{The modern de-facto standard HTTP server. Pronounce ``engine x''.}
\lsge{fastcgi}{FastCGI}{A standard protocol for interfacing interactive programs with a web server.}
\lsge{unicorn}{Unicorn}{A modern HTTP server for Rack applications.}
\lsge{rack}{Rack}{The de-facto standard interface for developing web applications in Ruby. Compare with FastCGI.}
\lsge{mongodb}{MongoDB}{The most popular document-oriented NoSQL database system.}
\lsge{redis}{Redis}{The most popular in-memory, key-value data store.}
\lsge{nosql}{NoSQL}{A schemaless way of storing data. Contrast with SQL.}
\lsge{cron}{NoSQL}{The classic UNIX time-based job scheduler.}
\lsge{unix}{UNIX}{The basis of most modern computer operating systems such as Linux.}
\lsge{linux}{Linux}{An open source implementation of UNIX.}
\lsge{ruby}{Ruby}{A dynamic object oriented programming language by Yukihiro Matsumoto. Gained a lot of popularity after being used to develop Ruby on Rails.}
\lsge{basecamp}{Basecamp}{A collaboration tool by 37Signals, from which the original Ruby on Rails framework was extracted.}
\lsge{macosx}{Mac OS X}{The operating system for Mac computers since 2001.}
\lsge{activerecord}{Active Record}{An architectural pattern for retrieving domain objects from relational databases, as well as the name for Ruby on Rail's implementation of that pattern.}
\lsge{scaffold}{Scaffold}{Generated code by Ruby on Rails used for rapid prototyping, includes model classes, database migrations, controllers and tests just by providing a model name and fields.}
\lsge{spam}{spam}{Unsoliciteded mass emails, famously named after a Monty Python sketch.}
\lsge{git}{Git}{Distributed revision control and SCM system}

% Acronym Definition
\lsad{abmc}{ABMC}{Asynchronous, Bi-directional Mass Communication}
\lsad{ajax}{AJAX}{Asynchronous JavaScript and XML}
\lsad{ide}{IDE}{Integrated Development Environment}
\lsad{imap}{IMAP}{Internet Message Access Protocol}
\lsad{smtp}{SMTP}{Simple Mail Transfer Protocol}
\lsad{zsh}{zsh}{Z Shell}
\lsad{vim}{Vim}{Vi IMproved}
\lsad{cli}{CLI}{Command-line interpreter}
\lsad{cgi}{CGI}{Common Gateway Interface}
\lsad{bcc}{BCC}{Blind Carbon Copy}
\lsad{php}{PHP}{PHP: Hypertext Preprocessor}
\lsad{rvm}{RVM}{Ruby Version Manager}
\lsad{cc}{CC}{Carbon Copy}
\lsad{crud}{CRUD}{Create, Read, Update, and Destroy}
\lsad{crm}{CRM}{Customer Relationship Management}
\lsad{dns}{DNS}{Domain Name System}
\lsad{dsl}{DSL}{Domain Specific Language}
\lsad{hci}{HCI}{Human-Computer Interaction}
\lsad{http}{HTTP}{HyperText Transfer Protocol}
\lsad{html}{HTML}{HyperText Markup Language}
\lsad{css}{CSS}{Cascading Style Sheets}
\lsad{ror}{Rails}{Ruby on Rails}
\lsad{saas}{SaaS}{Software as a Service}
\lsad{sql}{SQL}{Structured Query Language}
\lsad{ui}{UI}{User Interface}
\lsad{ip}{IP}{Internet Protocol}
\lsad{mvp}{MVP}{Minimal Viable Product}
\lsad{ux}{UX}{User Experience}
\lsad{uid}{UID}{Unique Identifier}
\lsad{uml}{UML}{Unified Modeling Language}
\lsad{url}{URL}{Uniform Resource Locator}
\lsad{coc}{CoC}{Convention over Configuration}
\lsad{dry}{DRY}{Don't Repeat Yourself}
\lsad{wet}{WET}{Write Everything Twice}
\lsad{orm}{ORM}{Object-relational Mapper}
\lsad{ses}{SES}{Simple Email Service}
\lsad{scm}{SCM}{Source Code Management}
\lsad{ai}{AI}{Artificial Intelligence}
\lsad{nlp}{NLP}{Natural Language Processing}

\makeglossaries