\chapter{Introduction}
\label{chapter:Introduction}

This is the introduction.

\section{Outline}

\textbf{This chapter} will give an overview and arguments for the relevance of new Email tools, as well the goals pursued by this thesis. Additionally, the structure of the work is explained.

In \textbf{\autoref{chapter:Technical}}, \textbf{\nameref{chapter:Technical}}, relevant technical background information is provided. The decision to build a web app is motivated. Standard-compliant email systems are explained and relevant standards are introduced. Lastly, an introduction to workflow systems and historic examples is given.

In \textbf{\autoref{chapter:Comparison}}, \textbf{\nameref{chapter:Comparison}},  two major categories of software -- dedicated mailmerge systems, and customer support systems -- are introduced, which overlap in functionality with Myriad.

In \textbf{\autoref{chapter:Concept}}, \textbf{\nameref{chapter:Concept}}, the architecture of the proposed system is motivated and its development process is highlighted.

In \textbf{\autoref{chapter:Implementation}}, \textbf{\nameref{chapter:Implementation}}, is concerned with technical details of how Myriad was implemented. The collaborative development process is described, as are actual system component and their functionality.

In \textbf{\autoref{chapter:Evaluation}}, \textbf{\nameref{chapter:Evaluation}}, Myriad's initial goals will be reiterated and contrasted with real world observed usage.

In \textbf{\autoref{chapter:Conclusion}}, \textbf{\nameref{chapter:Conclusion}},  the relevance of this system and the proposed framework is discussed; future work is outlined and possible directions proposed.

The conclusion is followed by a \textbf{\hyperref[chapter:Bibliography]{Bibliography}} of cited works and a \textbf{\hyperref[chapter:Figures]{List of Figures}}.

The \textbf{\nameref{part:Appendix}} contains selected source code, blabla, and a \textbf{\nameref{chapter:Colophon}}.



\section{Motivation}
\section{Goals and Background}